|

### 2023-02-15 paper_comparison/paper_comparison/paper_comparison.Rmd
fix the effect size formula

\small

\begin{gather}  \label{eq:effect-size}
E = E[E_{sample}|M],\\
E_{sample} = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}_a\boldsymbol{V})|}{|diag(\boldsymbol{R}_a\sigma^2)|} - n + tr(diag(\boldsymbol{R}_a\boldsymbol{V})^{-1}diag(\boldsymbol{R}_a\sigma^2)) + \boldsymbol{\mu}_z^{T}(\boldsymbol{R}_a\boldsymbol{V})^{-1}\boldsymbol{\mu}_z\right),\\
\boldsymbol{R}_a = \boldsymbol{I}_n - \boldsymbol{H}_a,\\
\boldsymbol{H}_a = \boldsymbol{X}_a(\boldsymbol{X}_a^T\boldsymbol{X}_a)^{-1}\boldsymbol{X}_a^T,
\end{gather}

>>>>

\footnotesize

\begin{gather}  \label{eq:effect-size}
E = E[E_{sample}|M],\\
E_{sample} = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}_a\boldsymbol{V}\boldsymbol{R}_a')|}{|diag(\boldsymbol{R}_a\sigma^2)|} - n + tr(diag(\boldsymbol{R}_a\boldsymbol{V}\boldsymbol{R}_a')^{-1}diag(\boldsymbol{R}_a\sigma^2)) + \boldsymbol{\mu}_z^{T}(\boldsymbol{R}_a\boldsymbol{V}\boldsymbol{R}_a')^{-1}\boldsymbol{\mu}_z\right),\\
\boldsymbol{R}_a = \boldsymbol{I}_n - \boldsymbol{H}_a,\\
\boldsymbol{H}_a = \boldsymbol{X}_a(\boldsymbol{X}_a^T\boldsymbol{X}_a)^{-1}\boldsymbol{X}_a^T,
\end{gather}
